---
title: "Chapter 4 Examples"
output: pdf_document
---

# Chapter Four Example problems

## Problem 54

First things first, we need to bring the data in.

```{r}
# Load Packages
##############
require(ggplot2)
require(magrittr)
cars <- read.table("C:\\Users\\Jonathan\\Google Drive\\Stats Camp\\Stine&Foster\\Data by Chapter\\Chapter 4\\04_cars\\04_cars.txt",
                   header = TRUE,
                   sep = "\t")
names(cars) <- c("displ", " trans", "name", "combinedMPG", "cityMPG", "hwyMPG", "cyl", "guzzler")
```

### Part A 

Draw a Histogram
```{r}
ggplot(data = cars, aes(x = combinedMPG)) +
  geom_histogram(binwidth = 3, color = "white", fill = "blue") +
  geom_histogram(data = cars[cars$guzzler == "G",] 
                 aes(x = combinedMPG),
                 color = "red",
                 fill = "lightblue",
                 binwidth = 1)

```
Upon examining the histogram we can see that the data has a tail off to the right hand side. This signifies that the histogram is right skewed. Thus, for our summary statistics, we should use the median as a messure of center and the IQR as a mesure of spread.

### Part B

```{r}
ggplot(data = cars, aes(x = guzzler, y = combinedMPG)) + 
  geom_boxplot(fill = "yellow", color = "blue") +
  coord_flip()
```




